%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Selected experiences}



%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%Future state prediction for mechanical systems using physics-informed neural networks,
%Oil and mineral predictions using semi-supervised clustering,
%Developing geophysical maps from satelite data using GANS, transfer learning and reversible neural networks,
%Energy/Force predictions for molecular systems using equivariant neural networks
%Image classification using spectral clustering and active learning
%Protein folding using self-trained transformer networks and NLP models

  \cventry
    {Machine learning highlights} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed novel \textbf{physics-informed graph neural networks} that allow the consideration of constraints and symmetries, and used them on mechanical and molecular systems to lower constraint violations by several orders of magnitudes, while increasing prediction accuracy.}
        \item {Developed novel \textbf{active learning} techniques for image classification and used them to significantly lower the amount of training images required for high accuracy.}
        \item {Developed novel \textbf{clustering} techniques to more accurately predict oil and mineral concentrations in the ground.}
%        \item {Built \textbf{natural language processing} and \textbf{convolutional} models and used self-training to teach them how amino acids bind together and how proteins fold.}
        \item {Used \textbf{transfer learning} and reversible networks to create geological maps from satellite data.}
%        \item {Predicted binding energies for molecular systems using physics-informed graph neural networks.}
        \item {Used \textbf{reinforcement learning} and Monte Carlo graph search techniques to create AIs that can play boardgames.}
        %\item {Designed MLOps framework for }
        %\item {Used PyRosetta to design protein bindings for KRAS.}
      \end{cvitems}
    }

\vspace{5mm}

%---------------------------------------------------------
  \cventry
  {Alexandra Institute} % Organization
  {AI specialist} % Job title
    {Aarhus, Denmark} % Location
    {Jan 2024 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {AI consultant on the project that won the AI Denmark award 2024.}
        \item {Designed and built a full framework for robotic movement and 3D bin packing.}
        \item {Developed a vehicle routing planner for a large Danish company.}
%        \item {Quantum computing specialist}
      \end{cvitems}
    }


  \cventry
  {Lind Capital} % Organization
  {Senior Machine Learning Engineer} % Job title
    {Aarhus, Denmark} % Location
    {June 2023 - Dec 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing and implementing open source MLOps platform.}
        \item {Building a global optimization framework.}
      \end{cvitems}
    }


  \cventry
  {Neural Solutions} % Organization
  {Owner -- Consultant} % Job title
    {Aarhus, Denmark} % Location
    {Dec 2021 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scoping of business problems solvable by machine learning.}
        \item {Designed tailored neural network architectures.}
      \end{cvitems}
    }


  \cventry
  {Proteic Bioscience Inc.} % Organization
  {Lead Machine Learning Specialist} % Job title
    {Vancouver, Canada} % Location
    {Jan 2022 - June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead developer of equivariant twice-differentiable neural networks for biomolecules.}
        \item {Developed MLOps framework with MLflow and Optuna for automatic data ingestion, processing and feature transforms, hyperparameter tuning and model tracking.}
        %\item {Used PyRosetta to design protein bindings for KRAS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {University of Bristish Columbia (UBC)} % Organization
  {Postdoctoral Research Fellow in Machine Learning} % Job title
    {Vancouver, Canada} % Location
    {May 2019 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed novel physics-informed neural networks inspired by differential algebraic systems of equations capable of honoring constraints and symmetries.}
        \item {Published reversible mimetic graph neural networks.}
        \item {Developed self-supervised conditional probability neural networks inspired by natural language processing models.}
        \item {Published a semi-supervised active learning algorithm utilizing pseudo-labeling which offers theoretical guarantees to be optimal.}
        \item {Deployed large-scale training on Amazon Web Services.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Computational Geoscience Inc.} % Organization
  {AI Research Scientist} % Job title
    {Vancouver, Canada} % Location
    {May 2019 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed clustering techniques for oil exploration.}
        \item {Published novel graph-based semi-supervised learning methods applied to seismic data.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {HydroGeophysics Group at Aarhus University} % Organization
  {Research Assistant} % Job title
    {Aarhus, Denmark} % Location
    {Aug 2017 - Nov 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{https://github.com/tueboesen/Sparse-iterative-parallel-linear-solver}{Open-sourced a sparse iterative parallel linear solver based on my research during my Ph.D.}}
        \item {\href{https://github.com/tueboesen/Parallelization-Framework}{Open-sourced an OpenMP parallelization framework developed during my Ph.D.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Danske Bank} % Organization
  {Analyst, Graduate Position} % Job title
    {Copenhagen, Denmark} % Location
    {Sep 2013 - Apr 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in customer insight creating forecast models.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {HydroGeophysics Group at Aarhus University} % Organization
  {Software Developer} % Job title
    {Aarhus, Denmark} % Location
    {Mar 2013 - Sep 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\href{https://hgg.au.dk/software/spia}{Created SPIA, an application for ground-based electromagnetic measurements.}}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
